Transfer of Value Functions via Variational Methods

### 2018-05-18 NIPS 2018/main.tex
new plots, added common legend

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{thmtools, thm-restate}
\usepackage{subcaption}
\usepackage{tikz}

@@

@@

\begin{figure*}[t] 
  \begin{subfigure}[b]{0.15\textwidth}
    %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
    \begin{tikzpicture}[scale=0.37]
\draw [white] (0,0) grid (7,7);
\begin{scope}[shift={(0,2)}]
\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);

@@

\draw [thick, gray] (0,0) rectangle (5,5);
\draw [line width=0.5mm, gray] (1.25,5/3) -- (5,5/3);
\draw [line width=0.5mm, gray] (0,5/3) -- (0.75,5/3);
\draw [line width=0.5mm, gray] (0,10/3) -- (3.25,10/3);
\draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);
\end{scope}
\end{tikzpicture} 
    \caption{}\label{f:rooms}
  \end{subfigure}
  \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{}\label{f:two_doors}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{}\label{f:one_door}
  \end{subfigure}
    \begin{subfigure}[b]{0.27\textwidth}
    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
    \caption{}\label{f:likelihood}
  \end{subfigure}
  \caption{(a) the rooms environment, (b) transfer from $10$ source tasks with both doors moving, (c) transfer from $10$ source tasks with only one door moving, and (d) transfer performance as a function of how likely the target task is according to the prior.}
  \label{fig:dipfdbsgraphplots}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{}\label{f:cartpole}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{}\label{f:mountaincar}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
    \caption{}\label{f:maze_results}
  \end{subfigure}
  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
  \label{fig:ccmazeplots}
\end{figure*}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{thmtools, thm-restate}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{color}

@@

\definecolor{nt}{RGB}{14, 90, 211}
\definecolor{gvt}{RGB}{188, 45, 20}
\definecolor{mgvt1}{RGB}{34, 170, 22}
\definecolor{mgvt3}{RGB}{160, 17, 163}

@@

\begin{figure*}[t] 
  \begin{subfigure}[b]{0.32\textwidth}
    %\includegraphics[trim=0.0cm 0.2cm 0.0cm 0.2cm,clip=true,height=2.6cm, width=2.0cm]{images/rooms2.pdf}
    \begin{tikzpicture}[scale=0.37]
\draw [white] (0,0) grid (11,8);
%\begin{scope}[shift={(0,2)}]
%\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
%\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
%\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
%\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);
%
%%\draw [fill=black!50] (1,1) circle [radius=0.1cm];
%%\node at (1,1) [ right] {$A$};
%
%\node at (1.8,-0.5)[left] {\color{darkgray}\small Start};
%\node at (3.1,5.5) [right]{\color{darkgray}\small Goal};
%
%\draw [thick, gray] (0,0) rectangle (5,5);
%\draw [line width=0.5mm, gray] (1.25,5/3) -- (5,5/3);
%\draw [line width=0.5mm, gray] (0,5/3) -- (0.75,5/3);
%\draw [line width=0.5mm, gray] (0,10/3) -- (3.25,10/3);
%\draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);

%\draw [thick, line width=0.6mm, dotted, nt] (5.5,4) -- (7,4);
%\node at (7,4) [right] {NT};
%\draw [thick, line width=0.6mm, dashed,gvt] (5.5,3) -- (7,3);
%\node at (7,3) [right] {GVT};
%\draw [thick, line width=0.6mm, mgvt1] (5.5,2) -- (7,2);
%\node at (7,2) [right] {1-MGVT};
%\draw [thick, line width=0.6mm, mgvt3] (5.5,1) -- (7,1);
%\node at (7,1) [right] {3-MGVT};

\begin{scope}[shift={(0,3)}]
\begin{scope}[shift={(3,0)}]
\draw [thick] (4,5) arc [radius=1, start angle=180, end angle= 270];
\path [fill=gray!50, very thin] (4,5) arc [radius=1, start angle=180, end angle= 270] -- (5,4) --(5,5)--(4,5);
\draw [thick] (0,1) arc [radius=1, start angle=90, end angle= 0];
\path [fill=lightgray!10, very thin] (0,1) arc [radius=1, start angle=90, end angle=0] -- (1,0) --(0,0)--(0,1);

@@

\draw [thick, gray] (0,0) rectangle (5,5);
\draw [line width=0.5mm, gray] (1.25,5/3) -- (5,5/3);
\draw [line width=0.5mm, gray] (0,5/3) -- (0.75,5/3);
\draw [line width=0.5mm, gray] (0,10/3) -- (3.25,10/3);
\draw [line width=0.5mm, gray] (3.75,10/3) -- (5,10/3);

\end{scope}

\draw [thick, line width=0.6mm, dotted, nt] (0,-1.5) -- (1,-1.5);
\node at (1.5,-1.5) [right] {NT};
\draw [thick, line width=0.6mm, dashed,gvt] (6, -1.5) -- (7,-1.5);
\node at (7,-1.5) [right] {GVT};
\draw [thick, line width=0.6mm, mgvt1] (0,-2.5) -- (1,-2.5);
\node at (1.5,-2.5) [right] {1-MGVT};
\draw [thick, line width=0.6mm, mgvt3] (6, -2.5) -- (7,-2.5);
\node at (11.2,-2.5) [left] {3-MGVT};

\end{scope}
\end{tikzpicture} 
    \caption{}\label{f:rooms}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room/lrev.pdf}
    \caption{Rooms Problem}\label{f:two_doors}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0cm 0cm 1.2cm 1.1cm,clip=true,height=2.9cm]{images/three-room-gen/lrev.pdf}
    \caption{Rooms Problem: Generalization}\label{f:one_door}
  \end{subfigure}
%    \begin{subfigure}[b]{0.27\textwidth}
%    \includegraphics[trim=0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/likelihood/lrew.pdf}
%    \caption{}\label{f:likelihood}
%  \end{subfigure}

	\begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
    \caption{Cartpole}\label{f:cartpole}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
    \caption{Mountain Car}\label{f:mountaincar}
  \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
    \includegraphics[trim=0.0cm 0cm 1.2cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
    \caption{Maze Navigation}\label{f:maze_results}
  \end{subfigure}
  \caption{Expected Return}
  \label{fig:ccmazeplots}

  \label{fig:dipfdbsgraphplots}
\end{figure*}

@@

%\begin{figure*}[t]
%  \begin{subfigure}[b]{0.32\textwidth}
%    \includegraphics[trim=0.0cm 0cm 1.8cm 1.3cm,clip=true,height=2.9cm]{images/cartpole/lrev.pdf}
%    \caption{}\label{f:cartpole}
%  \end{subfigure}
%    \begin{subfigure}[b]{0.32\textwidth}
%    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/mountaincar/lrev.pdf}
%    \caption{}\label{f:mountaincar}
%  \end{subfigure}
%    \begin{subfigure}[b]{0.32\textwidth}
%    \includegraphics[trim=0.0cm 0cm 1.6cm 1.3cm,clip=true,height=2.9cm]{images/maze/lrev_main.pdf}
%    \caption{}\label{f:maze_results}
%  \end{subfigure}
%  \caption{(a) Cartpole, (b) Mountain Car, and (c) Maze Navigation}
%  \label{fig:ccmazeplots}
%\end{figure*}
